\section{Optimization of Measurements}
The purpose of optimization of measurements is to reduce the impact caused by human or physical
hardware factors, i.e.\ delays that do not originate from the communication technology itself.

\subsection{Accuracy vs. Precision}
The quality of latency measurements can be evaluated in two dimensions: accuracy and
precision\cite{b13}.
For general measurements, accuracy will be considered as the magnitude of the difference
between the timestamp of the measurement result and the actual occurrence of the event,
i.e.\ the round trip time spent to transmit the data of the measurement result.
Precision is defined as the statistical variability between measurements, i.e.\ the degree
of variability and fluctuation of values between multiple measurement results.

\subsubsection{Hardware Timestamp}
Data reception on modern servers occurs asynchronously, i.e.\ the NIC receives the packet
first, then it is forwared to random access memory (RAM). Finally, the reception is
signaled to the CPU\cite{b13}.
Due to the interrupts caused by system calls of the OS\cite{b2}, the round-trip time
increases, resulting in a delay in the software timestamp, which further generates a
measurement latency and a significant decrease in the accuracy.

A feasible solution is to use hardware timestamps.
After the packet is received by the NIC itself, the hardware device responds with
the shortest clock to timestamp the packet accurately, since the hardware timestamp
is not affected by OS interrupts\cite{b13}.

\subsubsection{Measurement Error Tolerance}
According to the URLLC, the end-to-end latency must be
less than $\si{1}{ms}$ and the communication reliability must be greater
than 99.999\% etc.\cite{b3,b4,b5}.
Therefore, a slightly large error would cause a catastrophic impact on the latency
measurement results, e.g. an error of 1ms is enough to completely
change the optimization results under URLLC.

The usage of measurement systems with the highest possible precision to obtain more precise
measurement results is a basic prerequisite for scientific experiments.





